\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-19 doc/publications/plos16/supplementary_information.tex
updated 1000 project section and updated figure with new runtimes, also cleaned out supp table

 \hline
\multirow{3}{*}{phase3\_chr22: 2,504 x 1,103,548}   & \cursedforest & 0.06 & 4 min 2 seconds & \\  %240 &               &            &                  &                                                                \\
						  & RF - Spark ML   & 0.06 & 37 min 19 seconds  & \\  %2239
                                                    & randomForest - R        & NA         & NA               & NA\footnote{long vectors ($> 2^31-1$)  are not supported in the .Fortran interface} \\ %OK
                                                    & ranger - R    & 0.06       & 18 min        & 21GB (one processor) \\ %270
                                                    & ranger - c++ & 0.05  & 63 min &   \\
			                           & H2O           & 0.05       & 16 hours         & 600GB \footnote{java -Xmx600g -jar h2o.jar,   h2o.init(nthreads=20)} \\  %57600
\hline
\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest & 0.04  & 19 min 19 seconds &        \\ %1159   \cursedforest\ & 0.06 & 1hr 58min        & 4GB \\
                                                    & RF - Spark ML  &  0.04       & 8 hour 29 min   &     \\ % 3403 0.06       & 8hr 29min        & 8GB \\
  %                                                  & LR - Spark ML  &            & 2hr 6min         & 8GB \\
                                                   & ranger - R      & 0.05       & 1 hour 42 min          & num.threads=10 \\ %\footnote{don't know how to get the memory used, This was done on dpas-03} \\ %1680
                                                   & ranger - c++ & 0.04 & 5 hours 27 min &  \\
                                                    &H2O & NA & NA &   \\
\hline
\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest & 0.02  & 56 min 43 seconds     &        \\ %3403%& 0.04 & 4hr 0min                                             & 4GB \\
                                                    & RF - Spark ML  &  NA           &  NA                                                     & \\ %OK
  %                                                  & LR - Spark ML  &            & 14hr 48min                                           & 8GB \\
  						 & ranger - R      & 0.03      &    3 hour 58 min  &   \\ %14280

						 %DENIS: is it 6 h 58 m or the above quoted 3 h 58 m ? 
 %                                                   & ranger - R      &  0.03      & 58 mins\footnote{ but took 6 hours to load the data}
 %                                                                                                                                        & 909GB\footnote{I
  %                                                                                                                                         think
  %                                                                                                                                         this
  %                                                                                                                                         is
  %                                                                                                                                         total
   %                                                                                                                                        memory. The
   %                                                                                                                                        job
   %                                                                                                                                        was
   %                                                                                                                                        run
   %                                                                                                                                        with
    %                                                                                                                                               ntasks-per-node=160
     %                                                                                                                                      cores-per-socket=10
      %                                                                                                                                     on
       %                                                                                                                                    ruby
       %                                                                                                                                    }  \\
						%DENIS: our best result is on this subset is 10 min 49 seconds using 130 worker nodes, each with 8GB RAM so are you sure about the ranger result?
%						& ranger - R        &             0.027     &      03:58           &       pearcey --cpus-per-task=15 --mem 1600gb   906GB \\
						& ranger - c++ & 0.04 & 8 hours 54 min &  \\
\hline
\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & 0.01  & 3 hour 16min & \\% \\ %11760 %& 0.04 & 7hr 14min & 8GB \\
%& kmeans - Spark ML  & 0.18      & 30hr 44min    & 24GB \\ 
										& ranger - R       &        NA     &        NA   & \\
										& ranger - c++       &        NA     &        NA     &            80 CPU -- runs out of memory (12.8GB per CPU) \\
										& ranger - c++       &        NA     &        NA     &            160 CPU -- runs out of time at 20 hours \\
\hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{minipage}
\end{sidewaystable}

>>>>

 \hline
\multirow{3}{*}{phase3\_chr22: 2,504 x 1,103,548}   & \cursedforest & 0.06 & 4 min 2 seconds & \\  %240 &               &            &                  &                                                                \\
						  & RF - Spark ML   & 0.06 & 37 min 19 seconds  & \\  %2239
                                                    & randomForest - R        & NA         & NA               & NA\footnote{long vectors ($> 2^31-1$)  are not supported in the .Fortran interface} \\ %OK
                                                    & ranger - R    & 0.06       & 18 min        & 21GB (one processor) \\ %1080
                                                    & ranger - c++ & 0.05  & 1 hour 3 min &   \\  %3780
			                           & H2O           & 0.05       & 16 hours         & 600GB \footnote{java -Xmx600g -jar h2o.jar,   h2o.init(nthreads=20)} \\  %57600
\hline
\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest & 0.04  & 19 min 19 seconds &        \\ %1159   \cursedforest\ & 0.06 & 1hr 58min        & 4GB \\
                                                    & RF - Spark ML  &  0.04       & 8 hour 29 min   &     \\ % 3403 0.06       & 8hr 29min        & 8GB \\
  %                                                  & LR - Spark ML  &            & 2hr 6min         & 8GB \\
                                                   & ranger - R      & 0.05       & 1 hour 42 min          & num.threads=10  \\ %6120
                                                   & ranger - c++ & 0.04 & 5 hours 27 min &  \\ %19620
                                                    &H2O & NA & NA &   \\
\hline
\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest & 0.02  & 56 min 43 seconds     &        \\ %3403%& 0.04 & 4hr 0min                                             & 4GB \\
                                                    & RF - Spark ML  &  NA           &  NA                                                     & \\ %OK
  %                                                  & LR - Spark ML  &            & 14hr 48min                                           & 8GB \\
  						 & ranger - R      & 0.03      &    3 hour 58 min  &   \\ %14280
						& ranger - c++ & 0.04 & 8 hours 54 min &  \\ %32040
\hline
\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & 0.01  & 3 hour 16min & \\% \\ %11760 %& 0.04 & 7hr 14min & 8GB \\
%& kmeans - Spark ML  & 0.18      & 30hr 44min    & 24GB \\ 
										& ranger - R       &        NA     &        NA   & \\
										& ranger - c++       &        NA     &        NA     &            80 CPU -- runs out of memory (12.8GB per CPU) \\
										& ranger - c++       &        NA     &        NA     &            160 CPU -- runs out of time at 20 hours \\
\hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{minipage}
\end{sidewaystable}
